---
title: "TWRI PFAS Survey Data and Analysis Code"
output: github_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(survey)
```


[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.8132988.svg)](https://doi.org/10.5281/zenodo.8132988)

This is the data and code repository for the PFAS Public Survey study. 

Berthold, A., McCrary A., deVilleneuve, S., Schramm, M. In Submission.


This project uses the [renv](https://rstudio.github.io/renv/) and [targets](https://docs.ropensci.org/targets/) R packages to facilitate reproducibility. Once the project is downloaded and
opened in RStudio install the renv package:

```{r install, eval=FALSE}
install.packages("renv")
```

The packages and package versions used in the project can be installed and restored using:
```{r restore, eval=FALSE}
renv::restore()
```

To reproduce the analysis you will need a Census API key which can be obtained from https://api.census.gov/data/key_signup.html. Then use targets to rerun the analysis. This will take a little while to run:
```{r make, eval=FALSE}
tidycensus::census_api_key("API KEY GOES HERE")
targets::tar_make()
```

Survey responses used in our analysis are obtained with:

```{r data}
targets::tar_read(pfas_analysis_data)
```

Five models were fit in the analysis:

`m1`: Proportional odds model relating self-described knowledge about PFAS to demographic indicators and community PFAS exposure.

`m2`: Summary of 13 proportional odds models relating familiarity of 13 items with potential for PFAS contamination with demographic indicators and community PFAS exposure.

`m3`: Summary of 13 proportional odds models relating intention to change 13 items with potential for PFAS contamination with demographic indicators and community PFAS exposure.

`m4`: Logistic regression relating awareness of PFAS contamintion in drinking water with demographics, community PFAS exposure, and drinking water soruces.

`m5`: Proportional odds model relating levels of concern about PFAS in drinking water with demographics, drinking water sources, and awareness of drinking water contamination.

Model results can be obtained as follows:

```{r m1}
targets::tar_read(m1) |> summary()
```

`m1` and `m2` require some tidying:
```{r m2}
## each model is a row 1:13:
targets::tar_read(m2)$m[[1]] |> summary()
```


```{r}
renv::diagnostics()
```

