---
title: "Untitled"
format: html
---

```{r setup}
#| echo: false
#| message: false

library(readr)
library(janitor)
library(dplyr)
library(tidyr)
library(ggplot2)
library(twriTemplates)

```



## Data Import



```{r}
## grab responses
## need to skip first 3 rows
col_names <- read_csv("../data/PFAS_Survey_2023_04_13.csv", n_max = 0) |> 
  names()
PFAS_Results <- read_csv("../data/PFAS_Survey_2023_04_13.csv",
                         col_names = col_names,
                         skip = 3) |> 
  clean_names()

## grab questions
read_csv("../data/PFAS_Survey_2023_04_13.csv",
         n_max = 1) |> 
  clean_names() |> 
  select(starts_with("q"))

```


```{r}

```


The `echo: false` option disables the printing of code (only output is displayed).


1: is there a correlation between knowledge of community exposure to pfas (Q14) and live in communitvy impacted in by pfas (q14) familiarity with sources of pfas (q16) and changes in use of pfas (q17).

2: what are key factors that are correlated with an individual's perceived knowledge of pfas (q14)?
 - demographics, q 2-5 and 13,15,16,17



Analysis notes:

1: are survey results weighted. Probably need to use raking to weight sample means.
