---
title: "PFAS Survey Data Analysis"
format: 
  pdf:
    documentclass: article
    papersize: letter
author: Michael Schramm
date: today
#reference-doc: format.docx
bibliography: bibliography.yaml
csl: https://www.zotero.org/styles/council-of-science-editors-author-date?source=1
---

```{r setup}
#| echo: false
#| message: false
#| warning: false


knitr::opts_chunk$set(echo = FALSE,
                      dev = "ragg_png",
                      dpi = 300)
options(tidyverse.quiet = TRUE)
library(targets)
library(tidyverse)
library(anesrake)
library(flextable)
library(gtsummary)
library(officedown)
library(officer)
library(survey)
library(svyEffects)
library(twriTemplates)
library(kableExtra)

## if running in interactive, the store needs to be set to root directory
if(interactive()) {
  store = paste0("../", tar_path_store())
} else {
  store = tar_path_store()
}


# align legend function from claus wilke
# https://stackoverflow.com/questions/48000292/center-align-legend-title-and-legend-keys-in-ggplot2-for-long-legend-titles
align_legend <- function(p, hjust = 0.5)
{
  # extract legend
  g <- cowplot::plot_to_gtable(p)
  grobs <- g$grobs
  legend_index <- which(sapply(grobs, function(x) x$name) == "guide-box")
  legend <- grobs[[legend_index]]

  # extract guides table
  guides_index <- which(sapply(legend$grobs, function(x) x$name) == "layout")

  # there can be multiple guides within one legend box  
  for (gi in guides_index) {
    guides <- legend$grobs[[gi]]

    # add extra column for spacing
    # guides$width[5] is the extra spacing from the end of the legend text
    # to the end of the legend title. If we instead distribute it by `hjust:(1-hjust)` on
    # both sides, we get an aligned legend
    spacing <- guides$width[5]
    guides <- gtable::gtable_add_cols(guides, hjust*spacing, 1)
    guides$widths[6] <- (1-hjust)*spacing
    title_index <- guides$layout$name == "title"
    guides$layout$l[title_index] <- 2

    # reconstruct guides and write back
    legend$grobs[[gi]] <- guides
  }

  # reconstruct legend and write back
  g$grobs[[legend_index]] <- legend
  g
}

```



# Survey Demographic Profile

```{r}
#| label: tbl-demographics
#| tbl-cap: Demographic profile (unadjusted) of survey respondents.

unweighted_demo <- tar_read(pfas_analysis_data, store = store)
unweighted_demo |> 
  select(`Sex/Gender` = SEX,
         `Age` = AGEP,
         `Race/Ethnicity` = RACE5,
         `Educational` = SCHL) |> 
  mutate(Age = forcats::fct_na_value_to_level(Age, level = "No answer"),
         `Race/Ethnicity` = forcats::fct_na_value_to_level(`Race/Ethnicity`, level = "No answer"),
         Educational = forcats::fct_na_value_to_level(Educational, level = "No answer")) |> 
  tbl_summary(include = c(`Sex/Gender`, `Age`, `Race/Ethnicity`, `Educational`)) |>
  as_kable_extra(booktabs = TRUE, linesep = "") |> 
  kableExtra::kable_styling(latex_options = c("hold_position"))
  # as_flex_table() |>
  # style(pr_t = fp_text_default(font.size = 9), part = "body") |>
  # style(pr_t = fp_text_default(font.size = 9, bold = TRUE), part = "header") |> 
  # hline(i = 5, j = c(1:2), part = "body") |>
  # hline(i = 13, j = c(1:2), part = "body") |>
  # hline(i = 23, j = c(1:2), part = "body") |> 
  # set_table_properties(layout = "autofit") |> 
  # padding(padding.top = 0, padding.bottom = 0, part = "body") |> 
  # set_caption(caption = "Demographic profile (unadjusted) of survey respondents.",
  #             autonum = run_autonum(seq_id = "tab", bkm = "tabdemo"))
```



# Data Analysis

## Weighting

Prior to analysis, individual survey responses were weighted so that 
marginal proportions of the survey (`##r run_reference("tabdemo")`) matched 
national level benchmarks from the 5-year 2021 American Community Survey (ACS) 
on sex/gender, age group, race/ethnicity, and education level 
(`##r run_reference("tabweights")`). Weights on 
gender were developed by re-coding "female" and "other" responses as "non-male" 
because the ACS only provides binary response options for sex. Using this approach,
responses from both "female" and "other" respondents have the same marginal weight.
@kennedyUsingSexGender2022 provide substantial discussion on the treatment of 
sex and gender in survey adjustment. Due to small subpopulation sample sizes
within the Race/Ethnicity variable, Race/Ethnicity were recoded as 
White or Caucasian and Non-white categories. Weights were 
developed by poststratification raking using the American National Election 
Study (ANES) weighting algorithm implemented in the *anesrake* R package 
[@debellComputingWeightsAmerican2009; @pasekAnesrakeANESRaking2018].

```{r}
#| label: tbl-weights
#| tbl-cap: Marginal survey and target population proportions and marginal weighted values.
unweighted_demo <- tar_read(pfas_analysis_data, store = store)
unweighted_demo <- unweighted_demo |> 
  select(`Sex/Gender` = SEX_NM,
         `Age` = AGEP,
         `Race/Ethnicity` = RACE2,
         `Education` = SCHL) |> 
  mutate(`Sex/Gender` = forcats::fct_na_value_to_level(`Sex/Gender`, level = "No answer"),
         Age = forcats::fct_na_value_to_level(Age, level = "No answer"),
         `Race/Ethnicity` = forcats::fct_na_value_to_level(`Race/Ethnicity`, level = "No answer"),
         Education = forcats::fct_na_value_to_level(Education, level = "No answer")) |>
  tbl_summary(include = c(`Sex/Gender`, `Age`, `Race/Ethnicity`, `Education`),
              statistic = list(all_categorical() ~"{n}")) |>
  as_tibble() |>
  rename(`Unweighted N` = "**N = 1,100**",
         Value = "**Characteristic**") |>
  filter(!is.na(`Unweighted N`)) |>
  mutate(`Variable` = c(rep("Sex/Gender",3),
                        rep("Age", 7),
                        rep("Race/Ethnicity", 3),
                        rep("Education", 8)),
         `Unweighted N` = as.integer(`Unweighted N`)) |>
  group_by(Variable) |>
  mutate(`Unweighted %` = round(`Unweighted N` / sum(`Unweighted N`) * 100, 1)) |>
  select(Variable, Value, `Unweighted N`, `Unweighted %`)


weighted_demo <- tar_read(raked_weights, store = store) |>
  summary()



df <- tibble(
  demographic_indicators = list(`Sex` = as_tibble(weighted_demo$rk_SEX_NM,
                                                  rownames = "value") |>
                                  mutate(`Variable` = "Sex/Gender"),
                                `Race/Ethnicity` = as_tibble(weighted_demo$rk_RACE2,
                                                             rownames = "value") |>
                                  mutate(`Variable` = "Race/Ethnicity"),
                                `Age` = as_tibble(weighted_demo$rk_AGEP,
                                                  rownames = "value") |>
                                  mutate(`Variable` = "Age"),
                                `Education` = as_tibble(weighted_demo$rk_SCHL,
                                                        rownames = "value") |>
                                  mutate(`Variable` = "Education"))
)
weighted_demo <- df |>
  unnest(cols = c(demographic_indicators)) |>
  select(`Variable`, value, Target, `Wtd N`, `Wtd %`) |>
  filter(value != "Total") |>
  rename(Value = value) |>
  mutate(Target = round(Target * 100, 1),
         `Wtd N` = round(`Wtd N`, 1),
         `Wtd %` = round(`Wtd %` * 100, 1)) |>
  rename(`Target %` = Target,
         `Weighted N` = `Wtd N`,
         `Weighted %` = `Wtd %`)



weighted_demo <- unweighted_demo |>
  left_join(weighted_demo, by = c("Variable" = "Variable",
                                  "Value" = "Value")) |> 
  arrange(Variable)

weighted_demo |> 
  #select(!(Variable)) |> 
  rename(Characteristic = Value) |> 
  kableExtra::kbl(booktabs = T, linesep = "") |> 
  kableExtra::collapse_rows(columns = c(1,2),
                            latex_hline = "none",
                            row_group_label_position = "stack") |> 
  kableExtra::kable_styling(latex_options = "scale_down")
  #kableExtra::pack_rows(index = table(weighted_demo$Variable))
  # flextable() |>
  # merge_v(j = c("Variable")) |>
  # colformat_double(digits = 1) |>
  # hline(i = 3, j = c(2:7), part = "body") |>
  # hline(i = 10, j = c(2:7), part = "body") |>
  # hline(i = 13, j = c(2:7), part = "body") |>
  # style(pr_t = fp_text_default(font.size = 9), part = "body") |>
  # style(pr_t = fp_text_default(font.size = 9, bold = TRUE), part = "header") |>
  # set_table_properties(layout = "autofit") |>
  # padding(padding.top = 0, padding.bottom = 0, part = "body") |>
  # set_caption(caption = "Marginal survey and target population proportions and marginal weighted values.",
  #             autonum = run_autonum(seq_id = "tab", bkm = "tabweights"))
```


## Models

To explore factors associated with an individual's understanding of PFAS two
different proportional odds models [@agrestiCategoricalDataAnalysis2002] were developed
relating (1) self-described knowledge of PFAS (4 responses ranging from 
"I've never heard of it, and don't know what it is" to "I'm confident I know 
what it is"); and (2) awareness of potential sources of PFAS (5 responses ranging 
from "Not at all familiar" to "Extremely Familiar" to Sex/Gender, Age,
Race/Ethnicity, Education, and awareness of community exposure to PFAS (Yes, No, 
Not Sure). To explore factors associated with intended behavior change, a proportional
odds model was developed relating intention to change
use of items associated with PFAS (5 responses ranging from "will never change"
to "have already changed") to the same dependent variables.

The probability that an individual was aware of PFAS impacting their drinking water
was also explored. A logistic regression model was developed to relate awareness
of PFAS contamination in drinking water (a binary yes or no response) to Sex/Gender, Age,
Race/Ethnicity, Education, and awareness of community exposure to PFAS, and 
drinking water source (filtered tap water, unfiltered tap water, bottled water, other).
The last model evaluated the factors associated with an individuals level of 
concern about PFAS in their drinking water specifically. A proportional odds model
fit level of concern (5 responses ranging from "Not at all concerned" to 
"Extremely concerned") to Sex/Gender, Age,
Race/Ethnicity, Education, drinking water source, and awareness of PFAS
contamination in drinking water.

Model results are presented as odds-ratios (with approximate p-values calculated
by comparing the t-value against the standard normal distribution). Marginal 
effects are also presented as population-level predicted probabilities for a given
predictor estimated using observed values [@hanmerCurveClarifyingBest2013]. 
95% confidence intervals were derived using a parametric bootstrap as 
implemented in the *svyEffects* R package [@santosSvyEffectsSimulationBasedMarginal2023].
All models were fit using the *survey* package in R version 4.2.1
[@lumleyAnalysisComplexSurvey2004; @rcoreteamLanguageEnvironmentStatistical2022].


# Results


```{r}
#| label: tbl-q1819
#| tbl-cap: Summary of weighted survey responses to questions about PFAS knowledge and awareness of community exposure.
#| results: asis

tar_read(q16_19_tables, store = store) |> 
  select(Question, Response, proportion, proportion_se) |>
  filter(Question == "To your knowledge, has your community been exposed to PFAS?" |
           Question == "How would you describe your knowledge about PFAS as an environmental contaminant?" |
           Question == "What is your main source of drinking water?" |
           Question == "To your knowledge, has your primary source of drinking water been impacted by PFAS?"|
           Question == "How concerned are you about PFAS in your drinking water?") |>
  mutate(`Percent Response, SE` = case_when(
    is.na(proportion) ~ NA,
    .default = paste0(round(proportion * 100, 1),
                      ", ",
                      round(proportion_se * 100, 1)))) |>
  select(-c(proportion, proportion_se)) |>
  kableExtra::kbl(booktabs = T, linesep = "", escape = FALSE,
                  format = "latex") |> 
  kableExtra::column_spec(1, width = "20em") |> 
  kableExtra::column_spec(2, width = "20em") |> 
  kableExtra::collapse_rows(columns = c(1,2),
                            latex_hline = "linespace") |> 
  kableExtra::landscape()
  # flextable() |>
  # merge_v(j = c("Question")) |>
  # hline(i = 4, j = c(1:3), part = "body") |>
  # hline(i = 6, j = c(1:3), part = "body") |>
  # hline(i = 11, j = c(1:3), part = "body") |>
  # hline(i = 14, j = c(1:3), part = "body") |>
  # style(pr_t = fp_text_default(font.size = 9), part = "body") |>
  # style(pr_t = fp_text_default(font.size = 9, bold = TRUE), part = "header") |>
  # set_table_properties(layout = "autofit") |>
  # padding(padding.top = 0, padding.bottom = 0, part = "all") |>
  #   set_caption(caption = "Summary of weighted survey responses to questions about PFAS knowledge and awareness of community exposure.",
  #             autonum = run_autonum(seq_id = "tab", bkm = "tabq1819"))
  # 
  

```

Most respondents had no knowledge (41.1%) or were unsure (47.4%) if 
their community has been exposed to PFAS (`##r run_reference("tabq1819")`). 
Only 11.5% responded that they knew their community has been exposed to PFAS. 
When asked to describe knowledge level about PFAS, 45.1% responded that they 
have never heard of it and don't know what it is. An additional 31.6% responded 
they have heard of PFAS, but don't know what PFAS are.


```{r}
#| label: tbl-q20
#| tbl-cap: Summary of weighted responses to questions about awareness of different potential sources of PFAS.
q20_table <- tar_read(q16_19_tables, store = store) |> 
  select(Question, Response, proportion, proportion_se) |>
  filter(Question != "To your knowledge, has your community been exposed to PFAS?" &
           Question != "How would you describe your knowledge about PFAS as an environmental contaminant?" &
           Question != "What percentage of the U.S. population do you think has been exposed to PFAS?" &
           Question != "What is your main source of drinking water?" &
           Question != "To your knowledge, has your primary source of drinking water been impacted by PFAS?" &
           Question != "How concerned are you about PFAS in your drinking water?") |> 
  mutate(`Percent Response, SE` = case_when(
    is.na(proportion) ~ NA,
    .default = paste0(round(proportion,3) * 100,
                      "% (",
                      round(proportion_se, 3) * 100,
                      ")"))) |> 
  select(-c(proportion, proportion_se)) |> 
  pivot_wider(names_from = Response,
              values_from = `Percent Response, SE`)

kableExtra::kbl(q20_table)
# flextable(q20_table) |> 
#   style(pr_t = fp_text_default(font.size = 9), part = "body") |>
#   style(pr_t = fp_text_default(font.size = 9, bold = TRUE), part = "header") |>
#   set_table_properties(layout = "autofit") |> 
#   padding(padding.top = 0, padding.bottom = 0, part = "all") |> 
#   set_caption(caption = "Summary of weighted responses to questions about awareness of different potential sources of PFAS.",
#               autonum = run_autonum(seq_id = "tab", bkm = "tabq20"))

```

```{r}
#| echo: false
#| output: false
q19_summ <- tar_read(q16_19_tables, store = store) |> 
  select(Question, Response, proportion, proportion_se) |>
  filter(Question != "To your knowledge, has your community been exposed to PFAS?" &
           Question != "How would you describe your knowledge about PFAS as an environmental contaminant?" &
           Question != "What percentage of the U.S. population do you think has been exposed to PFAS?") |> 
  group_by(Response) |> 
  summarise(proportion = round(mean(proportion)*100,1))
q19_summ
```


On average, `r q19_summ$proportion[[1]]`% (minimum of 45% and maximum of 51.5%)
of respondents were "not at all familiar" with potential sources of PFAS 
included in the survey (`#r run_reference("tabq20")`). The probability of
response decreased for increasing levels of familiarity across all potential 
PFAS sources. Only `r q19_summ$proportion[[5]]`% (minimum of 5.9% and maximum of 
8.3%) of respondents, on average across all sources, responded "extremely 
familiar."

## General PFAS Awareness and Intent to Change Product Use



We did not find evidence for any association between Sex, Race/Ethnicity, 
and Education with self-described knowledge about PFAS 
(`#r run_reference("tabmodel1")`). We can't exclude potential Race/Ethnicity
sub-populations effects because Race/Ethnicity was collapsed into "White" and
"Non-white" categories. For example, all the respondents identifying as "Native
Hawaiian or Other Pacific Islander" (unweighted n = 3) responded that they had 
never heard of or knew what PFAS were. Some sub-populations might be more likely
to answer that they have less knowledge about PFAS. With the sample size used in
the current study we were not able to incorporate the sub-populations and develop
a model that would converge.



```{r}
#| label: tbl-model1
#| tbl-cap: Odds ratios and approximate p-values from proportional odds model explaining self-described knowledge of PFAS.
m1 <- targets::tar_read(m1, store = store)



olr_tidy <- function(x, ...) {
  broom::tidy(x, ...) %>%
    dplyr::mutate(
      p.value =
        pnorm(abs(statistic), lower.tail = FALSE) * 2
    )
}



tbl_regression(m1,
               exponentiate = TRUE,
               label = list(SEX ~ "Sex",
                            AGEP ~ "Age",
                            RACE2 ~ "Race/Ethnicity",
                            SCHL ~ "Education",
                            Q16 ~ "Community PFAS Exposure"),
               tidy_fun = olr_tidy) |>
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE) |> 
  as_kable_extra()
  # as_flex_table() |> 
  # style(pr_t = fp_text_default(font.size = 9), part = "body") |>
  # style(pr_t = fp_text_default(font.size = 9, bold = TRUE), part = "header") |>
  # style(pr_t = fp_text_default(font.size = 8), part = "footer") |>
  # set_table_properties(layout = "autofit") |>
  # padding(padding.top = 0, padding.bottom = 0, part = "all") |>
  # set_caption(caption = "Odds ratios and approximate p-values from proportional odds model explaining self-described knowledge of PFAS.",
  #             autonum = run_autonum(seq_id = "tab", bkm = "tabmodel1"))

```




There was not strong evidence for the influence of age on PFAS knowledge among
most of the age brackets (`#r run_reference("tabmodel1")`). However, there is 
evidence to support that someone in the 35:44 age bracket will respond with a 
higher self assessed knowledge level (OR = 1.63, p = 0.039) than someone in the 
reference bracket (18:24). There is also strong evidence that people aware of 
PFAS exposure in their communities self-report higher levels of knowledge about 
PFAS. People aware of PFAS exposure in their communities are 3.57 times 
and 4.35 times  more likely to respond with a higher self-assessed knowledge 
level than those responding "No" (OR = 0.28, p < 0.001) or "Not sure" 
(OR = 0.23, p < 0.001 ) to awareness of PFAS contamination in their communities.



```{r}
#| label: fig-m1margins
#| fig-height: 3
#| fig-width: 6.5
#| fig-dpi: 300
#| fig-cap: Average marginal predicted probabilities for self assessed knowledge of PFAS. Horizontal lines indicate the 95% confidence intervals of the marginal predicted probabilities.

marginal_m1 <- tar_read(marginal_m1, store = store)

p1 <- ggplot(marginal_m1$pred) +
  geom_pointrange(aes(y = y,
                      x = predicted,
                      xmin = conf.low,
                      xmax = conf.high,
                      color = Q16),
                  position = position_dodge(0.25),
                  size = 0.25,
                  alpha = 0.75) +
  scale_color_viridis_d(guide = guide_legend(
    title = "Awareness of Community\nPFAS Exposure",
    title.hjust = 1,
    label.hjust = 1,
    label.position = "left",
    reverse = TRUE
  )) +
  labs(x = "Probability", y = "") +
  theme_TWRI_print(base_family = "Arial") +
  theme(axis.text.y = element_text(size = 8, hjust = 1),
        # legend.background = element_rect(fill = alpha("black", 0.2),
        #                                  linewidth = 0),
        # legend.box.just = "right",
        legend.direction = "vertical",
        legend.position = c(0.79,0.85),
        legend.text = element_text(size = 8),
        # legend.text.align = 1,
        legend.title = element_text(size = 8),
        # legend.title.align = 1,
        strip.text = element_text(size = 8, face = "plain",
                                  hjust = 0,
                                  margin = margin(4.4, 4.4, 4.4, 40)))

cowplot::ggdraw(align_legend(p1, hjust = 1))

```

Marginal predicted probabilities show that someone that is aware of community
PFAS exposure is is much more likely to respond that they confidently 
know what PFAS (`r round(marginal_m1$preds$predicted[[4]],2)*100`%) are compared
to those that said their community hasn't been exposed 
(`r round(marginal_m1$preds$predicted[[8]],2)*100`%)
or don't know (`r round(marginal_m1$preds$predicted[[12]],2)*100`%;
Figure @fig-m1margins). Conversely, someone that is aware of community PFAS
exposure was much less likely to respond that they had never heard of PFAS and
didn't know what is was  (`r round(marginal_m1$preds$predicted[[1]],2)*100`%) 
compared to those that said their community hasn't been exposed 
(`r round(marginal_m1$preds$predicted[[5]],2)*100`%) or don't know 
(`r round(marginal_m1$preds$predicted[[9]],2)*100`%). We infer that respondents that
are aware of community PFAS exposure are most likely to respond that they have
at least heard of PFAS, but they may or may not be aware of what PFAS's are.
Respondents that are unaware or uncertain of community PFAS exposure are most
likley to have never heard of it, and if they have they don't know what it is.


```{r}
#| label: fig-m2margins
#| fig-height: 7.5
#| fig-width: 6.5
#| fig-dpi: 300
#| fig-cap: Average marginal predicted probabilities for an individual's familiarity with products that are associated with PFAS. Horizontal lines indicate the 95% confidence intervals of the marginal predicted probabilities.


## marginal effects of m2 controlled from demographics
marginal_m2 <- tar_read(marginal_m2, store = store)

ggplot(marginal_m2) +
  geom_pointrange(aes(y = y,
                      x = predicted, 
                      xmin = conf.low, 
                      xmax = conf.high, 
                      color = Q16),
                  position = position_dodge(0.25),
                  size = 0.25,
                  alpha = 0.75) +
  scale_color_viridis_d("Awareness of\nCommunity PFAS Exposure") +
  facet_wrap(~model, ncol = 3,
             labeller = labeller(model = label_wrap_gen(35)),
             as.table = FALSE,
             dir = "h") +
  labs(x = "Probability", y = "") +
  theme_TWRI_print(base_family = "Arial") +
  theme(axis.text.y = element_text(size = 8, hjust = 1),
        legend.direction = "vertical",
        legend.position = c(0.51,0.91),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 9, hjust = 0),
        strip.text = element_text(size = 8, face = "plain",
                                  hjust = 0,
                                  margin = margin(4.4, 4.4, 4.4, 40)))


  
```




```{r}
#| echo: false
#| output: false
marginal_m2_sum <- marginal_m2 |> 
  group_by(y, Q16) |> 
  summarise(predicted = mean(predicted))


marginal_m3 <- tar_read(marginal_m3, store = store)

marginal_m3_sum <- marginal_m3 |> 
  group_by(y, Q16) |> 
  summarise(predicted = mean(predicted))

marginal_m3_sum
```


Awareness of community PFAS exposure also show strong associations with 
familiarity of potential PFAS sources and intentions to change use of items 
with potential for PFAS contamination ([@fig-m2margins; @fig-m3margins]). On
average, `r round(marginal_m2_sum$predicted[[2]],2)*100`% and 
`r round(marginal_m2_sum$predicted[[2]],3)*100`% of those that were unaware of 
or not sure if their communties were contaminated by PFAS responded they were
"not familiar at all" with specific sources of PFAS contamination. This decreased 
to averages of `r round(marginal_m2_sum$predicted[[14]],2)*100`% and 
`r round(marginal_m2_sum$predicted[[15]],2)*100`% for the "extremely familiar"
response. On average, people that stated their communities were contaminated 
by PFAS had a lower probability (`r round(marginal_m2_sum$predicted[[1]],2)*100`%) 
of responding that they were "not familiar at all" and higher probability
(`r round(marginal_m2_sum$predicted[[13]],2)*100`%) of being "extremely 
familiar" with PFAS sources compared to the other two groups.

People indicating no or unsure of PFAS community contamination were on average
more likely to say they will never change their use of items 
(`r round(marginal_m3_sum$predicted[[2]],2)*100`% and 
`r round(marginal_m3_sum$predicted[[3]],2)*100`%) compared to those aware of
PFAS contamination in their community 
(`r round(marginal_m3_sum$predicted[[1]],2)*100`%;
[@fig-m3margins]). Those aware of community PFAS contamination were also
more likely on average to have already changed use of items 
(`r round(marginal_m3_sum$predicted[[13]],2)*100`%) relative to the other two
groups (`r round(marginal_m3_sum$predicted[[14]],2)*100`% for the "no" group and
`r round(marginal_m3_sum$predicted[[15]],2)*100`% for the "unsure" group).

```{r}
#| label: fig-m3margins
#| fig-height: 7.5
#| fig-width: 6.5
#| fig-dpi: 300
#| fig-cap: Average marginal predicted probabilities for an individual's intention to change use items associated with PFAS contamination. Horizontal lines indicate the 95% confidence intervals of the marginal predicted probabilities.'


## marginal effects of m2 controlled from demographics
marginal_m3 <- tar_read(marginal_m3, store = store)

ggplot(marginal_m3) +
  geom_pointrange(aes(y = y,
                      x = predicted, 
                      xmin = conf.low, 
                      xmax = conf.high, 
                      color = Q16),
                  position = position_dodge(0.25),
                  size = 0.25,
                  alpha = 0.75) +
  scale_color_viridis_d("Awareness of\nCommunity PFAS Exposure") +
  facet_wrap(~model, ncol = 3,
             labeller = labeller(model = label_wrap_gen(35)),
             as.table = FALSE,
             dir = "h") +
  labs(x = "Probability", y = "") +
  theme_TWRI_print(base_family = "Arial") +
  theme(axis.text.y = element_text(size = 8, hjust = 1),
        legend.direction = "vertical",
        legend.position = c(0.51,0.91),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 9, hjust = 0),
        strip.text = element_text(size = 8, face = "plain",
                                  hjust = 0,
                                  margin = margin(4.4, 4.4, 4.4, 40)))


  
```

## PFAS and Drinking Water


```{r}
#| label: tbl-model4
#| tbl-cap: Odds ratios and approximate p-values from logistic regression model explaining awareness of PFAS contamination in drinking water.
m4 <- targets::tar_read(m4, store = store)

tbl_regression(m4,
               exponentiate = TRUE,
               label = list(SEX ~ "Sex",
                            AGEP ~ "Age",
                            RACE2 ~ "Race/Ethnicity",
                            SCHL ~ "Education",
                            Q16 ~ "Community PFAS Exposure",
                            Q6 ~ "Drinking Water Source")) |>
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE) |>
  as_kable_extra()
  # as_flex_table() |>
  # style(pr_t = fp_text_default(font.size = 9), part = "body") |>
  # style(pr_t = fp_text_default(font.size = 9, bold = TRUE), part = "header") |>
  # style(pr_t = fp_text_default(font.size = 8), part = "footer") |>
  # set_table_properties(layout = "autofit") |>
  # padding(padding.top = 0, padding.bottom = 0, part = "all") |>
  # set_caption(caption = "Odds ratios and approximate p-values from logistic regression model explaining awareness of PFAS contamination in drinking water.",
  #             autonum = run_autonum(seq_id = "tab", bkm = "tabmodel4"))
```

There was not strong evidence that age, race, or education are predictive of
an individual's awareness of PFAS contamination in their drinking water 
(`#r run_reference("tabmodel4")`). For individuals identifying as other, the
odds of responding that they are aware their water is contaminated with PFAS was
100% lower (OR = 0, p < 0.001) than individuals identifying male. There was 
strong evidence for associations with both awareness of community PFAS exposure 
and drinking water sources. The odds that an individual aware of community PFAS
exposure indicated their drinking water was contaminated with PFAS was 100 times
greater than those that responded they were unaware of community PFAS exposure
(OR = 0.01, p < 0.001) and 8.3 times lower than those that were uncertain of
PFAS exposure (OR = 0.12, p = 0.003). These strong associations are indicative that 
awareness of community PFAS contamination may largely be attributed to contamination 
of drinking water supplies. Individuals with unfiltered tap water had 3.57 times
the odds of being aware that their drinking water was contaminated than those
with filtered tap water (OR = 0.28, p = 0.016).




```{r}
#| label: fig-m5margins
#| fig-height: 3
#| fig-width: 6.5
#| fig-dpi: 300
#| fig-cap: Average marginal predicted probabilities for concern about PFAS contamination in drinking water. Horizontal lines indicate the 95% confidence intervals of the marginal predicted probabilities.

marginal_m5 <- tar_read(marginal_m5, store = store)

p1 <- ggplot(marginal_m5$pred) +
  geom_pointrange(aes(y = y,
                      x = predicted,
                      xmin = conf.low,
                      xmax = conf.high,
                      color = Q9_6),
                  position = position_dodge(0.25),
                  size = 0.25,
                  alpha = 0.75) +
  scale_color_viridis_d(guide = guide_legend(
    title = "Awareness of\nDrinking Water Contamination",
    title.hjust = 1,
    label.hjust = 1,
    label.position = "left",
    reverse = TRUE
  )) +
  labs(x = "Probability", y = "") +
  theme_TWRI_print(base_family = "Arial") +
  theme(axis.text.y = element_text(size = 8, hjust = 1),
        # legend.background = element_rect(fill = alpha("black", 0.2),
        #                                  linewidth = 0),
        # legend.box.just = "right",
        legend.direction = "vertical",
        legend.position = c(0.79,0.20),
        legend.text = element_text(size = 8),
        # legend.text.align = 1,
        legend.title = element_text(size = 8),
        # legend.title.align = 1,
        strip.text = element_text(size = 8, face = "plain",
                                  hjust = 0,
                                  margin = margin(4.4, 4.4, 4.4, 40)))

cowplot::ggdraw(align_legend(p1, hjust = 1))


```

```
## notes

Add the following regression models:

Whats the probability of a response that drinking water has been impacted by PFAS (Q9.6) based on knowledge that community has been impacted by PFAS (Q16). Include drinking water source as a covariate (Q6).


What is the ordinal prob of response that a respondent is concerned about PFAS in *drinking water* (Q11.6) based on knowledge that drinking water has been impacted by PFAS (Q9.6).


```


# References
