---
title: "Data Analysis"
format: docx
author: Michael Schramm
date: today
reference-doc: format.docx
bibliography: bibliography.yaml
csl: https://www.zotero.org/styles/council-of-science-editors-author-date?source=1
---

```{r setup}
#| echo: false
#| message: false
#| warning: false


knitr::opts_chunk$set(echo = FALSE)
options(tidyverse.quiet = TRUE)
library(targets)
library(tidyverse)
library(anesrake)
library(flextable)
library(gtsummary)

## if running in interactive, the store needs to be set to root directory
if(interactive()) {
  store = paste0("../", tar_path_store())
} else {
  store = tar_path_store()
}

```



# Methods

## Survey

To do

```{r}
unweighted_demo <- tar_read(pfas_analysis_data, store = store)
unweighted_demo |> 
  select(`Sex/Gender` = SEX,
         `Age` = AGEP,
         `Race/Ethnicity` = RACE5,
         `Educational` = SCHL) |> 
  mutate(Age = forcats::fct_na_value_to_level(Age, level = "No answer"),
         `Race/Ethnicity` = forcats::fct_na_value_to_level(`Race/Ethnicity`, level = "No answer"),
         Educational = forcats::fct_na_value_to_level(Educational, level = "No answer")) |> 
  tbl_summary(include = c(`Sex/Gender`, `Age`, `Race/Ethnicity`, `Educational`)) |>
  as_flex_table() |>
  style(pr_t = fp_text_default(font.size = 9), part = "body") |>
  style(pr_t = fp_text_default(font.size = 9, bold = TRUE), part = "header") |>
  set_table_properties(layout = "autofit") |>
  hline(i = 5, j = c(1:2), part = "body") |>
  hline(i = 13, j = c(1:2), part = "body") |>
  hline(i = 23, j = c(1:2), part = "body")
```



## Data Analysis

Prior to analysis, individual survey responses were weighted so that 
marginal proportions of the survey matched national 
level benchmarks from the 5-year 2021 American Community Survey (ACS) on 
sex/gender, age group, race/ethnicity, and education level. Weights were 
developed by poststratification raking using the American National Election 
Study (ANES) weighting algorithm implemented in the *anesrake* R package 
[@debellComputingWeightsAmerican2009; @pasekAnesrakeANESRaking2018]. Weights on 
gender were developed by re-coding "female" and "other" responses as "non-male" 
because the ACS only provides binary response options for sex. Using this approach,
responses from both "female" and "other" respondents have the same marginal weight.
@kennedyUsingSexGender2022 provide substantial discussion on the treatment of 
sex and gender in survey adjustment.
@kennedyUsingSexGender2022 provide substantial discussion on the treatment of 
sex and gender in survey adjustment.



```{r}
unweighted_demo <- tar_read(pfas_analysis_data, store = store)
unweighted_demo <- unweighted_demo |> 
  select(`Sex/Gender` = SEX_NM,
         `Age` = AGEP,
         `Race/Ethnicity` = RACE5,
         `Educational` = SCHL) |> 
  mutate(`Sex/Gender` = forcats::fct_na_value_to_level(`Sex/Gender`, level = "No answer"),
         Age = forcats::fct_na_value_to_level(Age, level = "No answer"),
         `Race/Ethnicity` = forcats::fct_na_value_to_level(`Race/Ethnicity`, level = "No answer"),
         Educational = forcats::fct_na_value_to_level(Educational, level = "No answer")) |> 
  tbl_summary(include = c(`Sex/Gender`, `Age`, `Race/Ethnicity`, `Educational`),
              statistic = list(all_categorical() ~"{n}")) |>
  as_tibble() |>
  rename(`Unweighted N` = "**N = 1,100**",
         Value = "**Characteristic**") |> 
  filter(!is.na(`Unweighted N`)) |> 
  mutate(`Variable` = c(rep("Sex/Gender",3),
                        rep("Age", 7),
                        rep("Race/Ethnicity", 9),
                        rep("Education", 8)),
         `Unweighted N` = as.integer(`Unweighted N`)) |> 
  group_by(Variable) |> 
  mutate(`Unweighted %` = round(`Unweighted N` / sum(`Unweighted N`) * 100, 1)) |> 
  select(Variable, Value, `Unweighted N`, `Unweighted %`)


weighted_demo <- tar_read(raked_weights, store = store) |>  
  summary()



df <- tibble(
  demographic_indicators = list(`Sex` = as_tibble(weighted_demo$rk_SEX_NM,
                                                  rownames = "value") |> 
                                  mutate(`Variable` = "Sex/Gender"),
                                `Race/Ethnicity` = as_tibble(weighted_demo$rk_RACE5,
                                                             rownames = "value") |> 
                                  mutate(`Variable` = "Race/Ethnicity"),
                                `Age` = as_tibble(weighted_demo$rk_AGEP,
                                                  rownames = "value") |> 
                                  mutate(`Variable` = "Age"),
                                `Education` = as_tibble(weighted_demo$rk_SCHL,
                                                        rownames = "value") |> 
                                  mutate(`Variable` = "Education"))
)
weighted_demo <- df |> 
  unnest(cols = c(demographic_indicators)) |> 
  select(`Variable`, value, Target, `Wtd N`, `Wtd %`) |> 
  filter(value != "Total") |> 
  rename(Value = value) |> 
  mutate(Target = round(Target * 100, 1),
         `Wtd N` = round(`Wtd N`, 1),
         `Wtd %` = round(`Wtd %` * 100, 1)) |> 
  rename(`Target %` = Target,
         `Weighted N` = `Wtd N`,
         `Weighted %` = `Wtd %`)



unweighted_demo |> 
  left_join(weighted_demo, by = c("Variable" = "Variable", 
                                  "Value" = "Value")) |> 
  flextable() |> 
  merge_v(j = c("Variable")) |> 
  colformat_double(digits = 1) |> 
  set_table_properties(layout = "autofit") |> 
  hline(i = 3, j = c(2:7), part = "body") |> 
  hline(i = 10, j = c(2:7), part = "body") |> 
  hline(i = 19, j = c(2:7), part = "body") |> 
  style(pr_t = fp_text_default(font.size = 9), part = "body") |> 
  style(pr_t = fp_text_default(font.size = 9, bold = TRUE), part = "header")
```

